---
title: "Alcohol vs Seat choice"
author: "Aetan Barquero"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The number of people sitting in the middle is the highest when compared to people sitting in the front and the people sitting in the back. However, the standard deviation of the people sitting in the back is the highest compared to the people sitting in the front and teh middle. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Because the P value is such a low value (.0001) the chances of this happening with nothing strange occurring is extremely rare. 

```{r}
plot(TukeyHSD(model1))
```

The back row and front row are different because 0 is not in the confidence interval between the difference of the two. The middle and back and row are different as well. however the Middle and front are not different because the condifence interval is between zero. 

## Conclusions


